Calendar-based graphics for visualising people's daily schedules

### 2017-07-10 main.Rmd
Added to overlaying graph section

@@

>>>>

The comparison of one sensor to the other adds additional insights to the dataset, which is commonly done with an overlaying plot such as Figure \ref{fig:overlay}. For instance, the dominant patterns occurred to both train stations--Flinders Street Station and Flagstaff station--are together driven by the commuters on the work days; however, the former is overwhelmed by the number of pedestrians during the weekends and public holidays, compared to the latter. It suggests that Flagstaff station limits its functionality as simply the public transport hub for day-to-day commuters, but various activities take place around the Flinders Street Station other than commuting. Because Flinders Street Station closely lies to South Bank and other places of attractions where the locals go for leisure and the tourists for travelling.

@@

The nighttime events, such as White Night and New Year Evening Firework, has barely affected the operation of Flagstaff Station but heavily affected the incoming traffic to Flinders Street Station on these days.
